\section{Events \& Talks}
\cventry{Mar 2011}{conf.kde.in}{}{\small RVCE}{\small Bengaluru}{%
  \mybitem {First ever conference on KDE in India.}
  \mybitem {consisted of talks and workshops on Qt and KDE.}
}

\cventry{Mar 2011}{OSSCamp 11.03}{}{\small BBDNITM}{\small Lucknow}{Conducted hands-on session on GUI Application Development using C++ and Qt}
\cventry{Nov 2010}{OSSCamp 10.11}{}{\small JIIT}{\small Noida}{Participated.}

\cventry{Oct 2010}{Agile World Tour}{Impetus}{Noida}{}{%
 \mybitem {Organised by Agile Software Community of India}
 \mybitem {Consisted of talks evangelizing Agile Methodologies}
}

\cventry{Mar 2012}{LeThAc}{\small Conference organized at GGSIPU by its IEEE student branch}{}{}{%
  \mybitem{Introduced the audience, mainly students, to Software Versioning Control using Git}
}

\cventry{Jan 2012}{GIMP Workshop}{\small Organized by CIET at NCERT, New Delhi}{}{}{%
  \mybitem{Introduced Arts teachers from various schools around Delhi to GIMP during a day long workshop.}
}

\subsection {Events in Amity University, Noida}

\cventry{Jan 2011}{Geek Meetup}{\small Monthly Meeting of IITD-LUG Delhi}{}{}{%
  \mybitem{Hosted it in campus, with the help of ALiAS}
  \mybitem{Gave a talk on the \textbf{Best Partitioning scheme for a Distro Hopper} in which I discussed a partitioning scheme which allows me to manage multiple operating systems on one computer.}
}

\cventry{Feb 2010}{P2P}{\small Organized by AmiSUN}{}{}{%
  \mybitem{Gave an \textbf{Introductory talk on Linux}}
  \mybitem{Was a fellow co-ordinator of the event.}
}

\cventry{Sep 2009}{Software Freedom Day} {\small Organized by AmiSUN}{}{}{%
  \mybitem{Talked about how one can use \textbf{Linux on Virtual Box} without tampering with the host OS}
  \mybitem{Was a fellow co-ordinator of the event.}
}

\cventry{Jan 2010}{Workshop on Linux Basics}{\small Organized by SecureCon}{}{}{%
  \mybitem {Was invited by SecureCon, Network Security Club @Amity for the workshop.}
  \mybitem {Workshop aimed for providing a kick-start so that members could begin working with BackTrack Linux.}
}

\cventry{Sep 2010}{TechWeek}{\small Organized by Amity IT IEEE Club}{}{}{%
  \mybitem {In ``\textbf{Why use Linux}'' I emphasised on benefits of using Linux.}
  \mybitem {Was invited for the talk.}
}

\cventry{Sep 2008}{Software Freedom Day Celebrations}{\small Organized by AmiSUN}{}{}{%
 \mybitem {Was a co-ordinator.}
 \mybitem {Event consisted of competitions, workshops and seminars.}
}

\cventry{Feb 2010}{Amity Cultural and Technical Festival (ACT 2010)}{}{}{}{%
  \mybitem{Co-ordinated a programming competition called \textbf{TUX-WARS}, organized by ALiAS, which required participants to code on Linux platform.}
  \mybitem{Participated in a technical crossword competition called \textbf{MindBoggler} and secured first prize.}
  \mybitem{Participated in a \textbf{Debugging} competition and secured second prize.}
}

\cventry{Feb 2012}{Amity Youth Festival (AYF 2012)}{}{}{}{%
  \mybitem{Co-ordinated two competitions, GeekBattle (online) and FOSS Quiz (offline) organized by the Linux Club (ALiAS).}
  \mybitem{As the trainer, attended the two day workshop on ``Android app development using Python'' organized by the IT Department.}
}

\cventry{Feb 2011}{Amity Cultural Technical Festival (ACT 2011)}{}{}{}{Co-ordinated an two day event called \textbf{FOSS Camp}, organized by ALiAS. Participants came in from all over Delhi-NCR and had fun hacking on and talking about Open Source technologies}


\cventry{Jan 2010}{Confluence - The Next Generation IT Summit}{\small Organized by ASET IT Department}{}{}{Was a student volunteer.}

\cventry{Sep 2010}{Corporate Meet}{\small Organized by Corporate Resource Center, ASET}{}{}{Was a student volunteer.}

\cventry{Feb 2011}{National Conference on Advances in Computer Science and Technology}{\small Organized by ASET CSE Department}{}{}{Was a student volunteer.}
